# Coding data

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(patchwork)

theme_set(theme_classic(base_size = 12) +
            theme(plot.background = element_rect(fill = NA, color = NA),
                  strip.background = element_rect(color = NA),
                  legend.background = element_rect(fill = NA)))

## load transcript data:
transcript <- read_excel("../data/arg2 transcript.xlsx")[-1,][1:297,] %>%
  select(
    subject,
    card_no,
    rare,
    slotA_filled,
    slotL_filled,
    current_arms,
    current_legs,
    move
  )

## load subject data:
subjects <- read_excel("../data/arg2 participants.xlsx") %>%
  select(
    subject,
    dob,
    date,
    condition,
    drop
  ) %>%
  mutate(
    subject = as.integer(subject),
    condition = as.factor(condition),
    dob = ymd(dob),
    date = ymd(date),
    age = as.numeric(date - dob) / 365.25,
    drop = as.logical(drop)
  ) %>%
  ## remove dropouts:
  filter(is.na(drop)) %>%
  select(-drop)

## load coding reference sheet:
states_actions <- read_excel("states and actions.xlsx",
                             range = "B3:L84") %>% 
  select(-`_`)
```

Evaluate each move in the transcript as to whether it violates relevance, risks losing a rare card, or squanders search cost.

```{r}
## create long form of lookup table for easy joining (= looking up), add
## 'alternatives' columns to evaluate whether an OK move was the alternative to
## a costly/irrelevant/risky move:
coding_table <- states_actions %>%
  pivot_longer(new:aL, names_to = "move", values_to = "evaluation") %>% 
  group_by(rare, slotA_filled, slotL_filled, current_arms, current_legs) %>% 
  mutate( alt_irrel = TRUE %in% str_detect(evaluation, "irrel"),
          alt_cost  = TRUE %in% str_detect(evaluation, "cost"),
          alt_Rcert = TRUE %in% str_detect(evaluation, "Rcert"),
          alt_Rposs = TRUE %in% str_detect(evaluation, "Rposs")) %>% 
  ungroup

## do evaluation - match each line of the transcript to the coding table, look
## up how the move is to be evatuated and what errors "were available":
transcript_evaluated <- transcript %>% 
  left_join(coding_table,
            by = c("rare", "slotA_filled", "slotL_filled", "current_arms", "current_legs", "move") )
```

# Summary

## Summarize each type of error

... and "omission of errors" for each participant.

```{r}
ptcp_scores <- transcript_evaluated %>% 
  group_by(subject) %>% 
  summarize( relevance_related = sum(alt_irrel),
             irrelevant        = sum(str_detect(evaluation, "irrel")),
             relevant          = relevance_related - irrelevant,
             ##
             cost_related = sum(alt_cost),
             cost_wasting = sum(str_detect(evaluation, "cost")),
             cost_saving  = cost_related - cost_wasting,
             ##
             risk_related  = sum(alt_Rcert) + sum(alt_Rposs),
             risk_insens   = sum(str_detect(evaluation, "R....")),
             risk_sens     = risk_related - risk_insens )
```

Join transcription codes with subject data.

```{r}
d <- subjects %>% 
  left_join(ptcp_scores, by = "subject") %>% 
  select( -c(dob, date) )
```

Plot.

```{r}
plot_triptych <- d %>%
  select( -c(irrelevant, risk_insens, cost_wasting) ) %>% 
  pivot_longer( c(relevance_related:risk_sens) ) %>% 
  mutate(aspect = as.factor(name),
         name = NULL,
         aspect = fct_collapse( aspect,
                                relevance = c("relevance_related", "relevant"),
                                risk = c("risk_related", "risk_sens"),
                                cost = c("cost_related", "cost_saving") ),
         variable = rep(c("N", "count"), length.out = n() )) %>% 
  pivot_wider(names_from = variable, values_from = value)

head(plot_triptych)
```

```{r}
levels(plot_triptych$aspect) <- c("(a) Cost-sensitivity", "(b) Relevance-sensitivity", "(c) Risk-sensitivity")

gg_triptych <- ggplot(plot_triptych,
                      aes(x = age,
                          y = count / N,
                          size = N)) +
  geom_abline(intercept = .5, slope = 0, linetype = "8414", alpha = .3, size = 1) +
  geom_point(fill = "#d00a55",
             alpha = .3,
             shape = 21) +
  geom_point(color = "black",
             shape = 1) +
  #geom_text( aes(label = subject,
  #               x = age + .4),
  #           size = 3) +
  scale_y_continuous(limits = c(0, 1)) +
  facet_grid(. ~ aspect) +
  labs(size = "No. of\ndecisions", x = "Age", y = "Proportion adaptive information choices") +
  theme(panel.background = element_rect(color = "grey70"),
        strip.text = element_text(size = 9))

ggsave(plot = gg_triptych, filename = "plots/cogsci_arg2.png", width = 18, height = 6, units = "cm", dpi = 600)
gg_triptych
```

# Azzu's 3 summaries

## First first moves

Number of children who queried Arms vs. Legs as their very first move:

```{r}
A_very_firsts <- transcript %>%
  group_by( subject, rare ) %>% 
  summarize( very_first_move = move[1] ) %>% 
  group_by( rare ) %>% 
  summarize( arms = sum(very_first_move == "qA"),
             legs = sum(very_first_move == "qL") )
```

## First moves per card while A slot is open

```{r}
A_card_firsts <- transcript %>%
  filter( slotA_filled == "false" ) %>%
  group_by( subject, card_no, rare ) %>% 
  summarize( card_first_move = move[1] ) %>% 
  group_by( subject, rare ) %>% 
  summarize( arms_first = sum(card_first_move == "qA"),
             legs_first = sum(card_first_move == "qL")) %>%
  ungroup %>% 
  mutate( p_arms_first = arms_first / (arms_first + legs_first))
```

## All queries of arms vs. legs while A slot is open

```{r}
A_slotA_open <- transcript %>%
  filter( slotA_filled == "false" ) %>% 
  group_by( subject, card_no, rare ) %>% 
  summarize( arm_queries = sum(move == "qA"),
             leg_queries = sum(move == "qL") ) %>% 
  ungroup %>% 
  group_by( subject, rare ) %>% 
  summarize( arm_queries = sum(arm_queries),
             leg_queries = sum(leg_queries) ) %>% ungroup %>% 
  mutate( p_arm_queries = arm_queries / (arm_queries + leg_queries) )
```

## Plot the latter two

Prepare plot data frames:

```{r}
levels(subjects$condition) <- c("Uniform", "Skewed")

plot_A_card_firsts <- A_card_firsts %>% 
  left_join(subjects, by = "subject") %>% 
  select( -c(dob, date, rare) )

plot_A_slotA_open <- A_slotA_open %>% 
  left_join(subjects, by = "subject") %>% 
  select( -c(dob, date, rare) )
```

Plot first within-card moves:

```{r warning=FALSE}
gg_A_firsts <- ggplot(plot_A_card_firsts,
       aes(x = age,
           y = p_arms_first,
           fill = condition,
           size = arms_first + legs_first)) +
  geom_point( alpha = .7,
              color = "black",
              shape = 21 ) +
  geom_abline(slope = 0, intercept = .5, linetype = "8424", size =.5, alpha = .4) +
  scale_fill_manual(values = c("#4488ff", "#ff8844")) +
  ylim(c(0, 1)) +
  guides(size = F) +
  labs(y = "proportion across cards of querying arms first",
       title = "All first moves")
#ggsave(plot = gg_A_firsts, filename = "plots/first_move_within_cards.png",
#       width = 8, height = 5, units = "cm", dpi = 600)
```

Plot all arm queries while the arm slot was open:

```{r warning=FALSE}
gg_A_queries <- ggplot(plot_A_slotA_open,
       aes(x = age,
           y = p_arm_queries,
           fill = condition,
           size = arm_queries + leg_queries)) +
  geom_point( alpha = .7,
              color = "black",
              shape = 21 ) +
  geom_abline(slope = 0, intercept = .5, linetype = "8424", size = .5, alpha = .4) +
  scale_fill_manual(values = c("#4488ff", "#ff8844")) +
  ylim(c(0, 1)) +
  guides(size = F) +
  labs(y = "proportion arm queries while arm slot open",
       title = "All queries (1st and 2nd per card)")
#ggsave(plot = gg_A_queries, filename = "plots/arm_queries_with_open_Aslot.png",
#       width = 8, height = 5, units = "cm", dpi = 600)
```

Plot both:

```{r}
gg_out <- gg_A_firsts + gg_A_queries
ggsave(plot = gg_out, filename = "plots/first_and_seconds.png",
       width = 16, height = 5, units = "cm", dpi = 600)
```

# Stats on fist moves

First-card first moves:
```{r}
very_first <- transcript_evaluated %>%
  filter( card_no == 1 ) %>% 
  group_by( subject, rare ) %>% 
  summarize( first_move = move[1] ) %>% 
  filter( first_move != "new" ) %>% 
  ungroup
table(very_first$first_move, very_first$rare)
```


All within-card first moves:
```{r}


table(firsts_test$first_move, firsts_test$rare )
```

Ratios per child in Skewed, before any slot gets filled, of looking at arms vs. legs:
```{r}
child_ratios_empty <- transcript_evaluated %>% 
  filter( slotA_filled == "false" & slotL_filled == "false") %>% 
  group_by( subject, card_no, rare ) %>% 
  summarize( first_move = move[1] ) %>% 
  filter( first_move != "new" ) %>% 
  group_by( subject, rare ) %>% 
  summarize( ratio_arms = sum(first_move == "qA") / n() ) %>% 
  ungroup

ggplot(child_ratios_empty,
       aes(x = rare,
           y = ratio_arms )) +
  geom_dotplot(stackdir = "center",binaxis = "y")
#ggsave("plots/perchild_ratios.png")

child_ratios_empty %>% 
  group_by( rare ) %>% 
  summarize( ratio_m = mean(ratio_arms) )


```

Now for the second card:
```{r}
child_second_card_empty <- transcript_evaluated %>% 
  filter( slotA_filled == "false" & slotL_filled == "false" & card_no == 2 & rare == "A") %>% 
  group_by( subject ) %>% 
  summarize( first_move = move[1] ) %>% 
  ungroup

table(child_second_card_empty$first_move)
```

Whatever kids did with first card:
```{r}
child_first_cards <- transcript_evaluated %>% 
  filter( rare == "A" & card_no == 1 )
```




```{r}
transcript_evaluated %>%
  group_by( rare ) %>%
  summarize( risk    = sum(evaluation %in% c("Rposs", "Rcert")),
             risk_N  = sum(alt_Rcert) + sum(alt_Rposs),
             cost    = sum(evaluation=="cost"),
             cost_N  = sum(alt_cost),
             irrel   = sum(evaluation=="irrel"),
             irrel_N = sum(alt_irrel) )
```

